### 2014-10-08 fundamentals/impl.tex
describe decay shortcut

    \item "lazy" (future) decays any material whenever its composition is
        viewed (e.g. an agent queries information about a material's
        $^{239}Pu$ content).

@@

\TODO{describe decay algorithm and how it might be improved}.

>>>>

    \item "lazy" (future) decays any material whenever its composition is
        viewed (e.g. when an agent queries information about a material's
        $^{239}Pu$ content).

@@

In order to avoid excess decay calculations, when a material's decay function
is invoked, the material checks to see if it contains any nuclides with decay
constants that are significant with respect to the time delta for the current
decay operation.  If all the decay constants are not significant, no decay
calculation is performed and the material remains unchanged.  This error does
not accumulate because the next time the material's decay function is invoked,
the time delta will be larger. \TODO{want more detail on this decay shortcut?}
\TODO{describe decay algorithm and how it might be improved}.
